---
title: "STA426_FS2020: Exercise 1"
author:
- name: Elyas Heidari
  affiliation: 
  - &IMLS Institute for Molecular Life Sciences, University of Zurich, Switzerland
  - Swiss Institute of Bioinformatics (SIB), University of Zurich, Switzerland
date: '`r format(Sys.Date(), "%B %d, %Y")`'
output:
  workflowr::wflow_html:
    code_folding: hide
    toc: true
    toc_float: true
    number_sections: false
---

<!-- 2020-09-14 11:40 -->
<!-- elihei  [<eheidari@student.ethz.ch>]-->
<!--/Volumes/Projects/STA426_FS2020/analysis/EX_1_2020_09_14.Rmd-->

# Setup
```{r setup, include = FALSE}
library('BiocStyle')
knitr::opts_chunk$set( autodep=TRUE, cache=TRUE, dev='png', cache.lazy = FALSE)
# wflow_build(files='analysis/EX_1_2020_09_14.Rmd', view=F, verbose=T)
```

# Log-normal samples
**Q:** Create an HTML document that samples 100 values from a log-normal distribution (say, `mu=1`, `sigma=.25`); create a histogram of the distribution and the distribution on the log scale; report the mean and variance of the sample in line in the text. In general, do not just dump the R code and plots in the HTML document; break your exercises into sections with headings, add some text and make it readable.

**A:**

```{r test1, message=FALSE, warning=FALSE, paged.print=FALSE}
# sample from log-normal
n          = 100
ln_samples = rlnorm(n, meanlog=1, sdlog=0.25)
ln_hist    = hist(ln_samples, xlab='value')
ln_hist$counts = log(ln_hist$counts, 2)
plot(ln_hist, xlab ='log value')
summary(ln_samples)
mean_s     = mean(ln_samples)
var_s      = var(ln_samples)
```
The sample has mean `r mean_s` and variance `r var_s`.

# Session info